El Mayor Postseismic \author{Trever Hines} \rule{\headwidth}{1.0pt}

### 2016-03-27 RoughDraft/ElMayor.tex
commit before push

\usepackage{amssymb,amsmath}
\usepackage[margin=1.0in]{geometry}
\usepackage{fancyhdr} % required for custom header
\usepackage{graphicx}
\usepackage{listings}
\usepackage{courier}
\usepackage[usenames,dvipsnames]{color}
\usepackage[maxfloats=50]{morefloats}

@@

@@

\begin{figure}
\includegraphics[scale=0.6]{Figures/near_field_data_1}
\centering 
\caption{near field coseismic}
\label{nearfield1}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{Figures/near_field_data_2}
\centering 
\caption{near field coseismic}
\label{nearfield2}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{Figures/near_field_data_3}
\centering 
\caption{near field coseismic}
\label{nearfield3}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{Figures/near_field_data_4}
\centering 
\caption{near field coseismic}
\label{nearfield4}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{Figures/far_field_data_1}
\centering 
\caption{near field coseismic}
\label{farfield1}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{Figures/far_field_data_2}
\centering 
\caption{near field coseismic}
\label{farfield2}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{Figures/far_field_data_3}
\centering 
\caption{near field coseismic}
\label{farfield3}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{Figures/far_field_data_4}
\centering 
\caption{near field coseismic}
\label{farfield4}
\end{figure}

\begin{figure}
\includegraphics[scale=0.8]{Figures/near_field_record_section}
\centering 
\caption{near field record section}
\label{NearFieldRS}
\end{figure}
\begin{figure}
\includegraphics[scale=0.8]{Figures/far_field_record_section}
\centering 
\caption{far field record section}
\label{FarFieldRS}
\end{figure}        
\begin{figure}

@@

\begin{figure}
\includegraphics[scale=0.1]{Figures/final_coseismic}
\centering 
\caption{misfit with different shear modulus ratios}
\label{ShearRatio}
\end{figure}

\begin{figure}
\includegraphics[scale=0.1]{Figures/final_afterslip_0-1}
\centering 
\caption{misfit with different shear modulus ratios}
\label{ShearRatio}
\end{figure}

\begin{figure}
\includegraphics[scale=0.1]{Figures/final_afterslip_1-3}
\centering 
\caption{misfit with different shear modulus ratios}
\label{ShearRatio}
\end{figure}

\begin{figure}
\includegraphics[scale=0.1]{Figures/final_afterslip_3-5}
\centering 
\caption{misfit with different shear modulus ratios}
\label{ShearRatio}
\end{figure}

>>>>

\usepackage{amssymb,amsmath}
\usepackage[margin=1.0in]{geometry}
\usepackage{fancyhdr} % required for custom header
\usepackage{graphicx}
\usepackage{listings}
\usepackage{courier}
\usepackage[usenames,dvipsnames]{color}
\usepackage[maxfloats=30]{morefloats}
\usepackage{caption}
\usepackage{subcaption}

@@

\begin{figure}
\includegraphics[scale=0.9]{Figures/context_map}
\centering 
\caption{}
\label{ContextMap}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{Figures/near_field_data_1}
\centering 
\caption{}
\label{nearfield1}
\end{figure}
\begin{figure}
\includegraphics[scale=0.6]{Figures/near_field_data_2}
\centering 
\caption{}
\label{nearfield2}
\end{figure}
\begin{figure}
\includegraphics[scale=0.6]{Figures/near_field_data_3}
\centering 
\caption{}
\label{nearfield3}
\end{figure}
\begin{figure}
\includegraphics[scale=0.6]{Figures/near_field_data_4}
\centering 
\caption{}
\label{nearfield4}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6,resolution=10]{Figures/far_field_data_1}
\centering 
\caption{}
\label{farfield1}
\end{figure}
\begin{figure}
\includegraphics[scale=0.6,resolution=10]{Figures/far_field_data_2}
\centering 
\caption{}
\label{farfield2}
\end{figure}
\begin{figure}
\includegraphics[scale=0.6,resolution=10]{Figures/far_field_data_3}
\centering 
\caption{}
\label{farfield3}
\end{figure}
\begin{figure}
\includegraphics[scale=0.6,resolution=10]{Figures/far_field_data_4}
\centering 
\caption{}
\label{farfield4}
\end{figure}

\begin{figure}
\includegraphics[scale=0.9]{Figures/near_field_record_section}
\centering 
\caption{near field record section}
\label{NearFieldRS}
\end{figure}
\begin{figure}
\includegraphics[scale=0.9]{Figures/far_field_record_section}
\centering 
\caption{far field record section}
\label{FarFieldRS}
\end{figure}        
\begin{figure}

@@

\begin{figure}
\includegraphics[scale=0.1]{Figures/final_coseismic}
\centering 
\caption{}
\label{FinalCoseismic}
\end{figure}

\begin{figure}
\includegraphics[scale=0.1]{Figures/final_afterslip_0-1}
\centering 
\caption{}
\label{ShearRatio}
\end{figure}

\begin{figure}
\includegraphics[scale=0.1]{Figures/final_afterslip_1-3}
\centering 
\caption{}
\label{ShearRatio}
\end{figure}

\begin{figure}
\includegraphics[scale=0.1]{Figures/final_afterslip_3-5}
\centering 
\caption{}
\label{ShearRatio}
\end{figure}

\begin{figure}
\includegraphics[scale=0.9]{Figures/near_field_final_record_section}
\centering 
\caption{}
\label{ShearRatio}
\end{figure}

\begin{figure}
\includegraphics[scale=0.9]{Figures/far_field_final_record_section}
\centering 
\caption{}
\label{ShearRatio}
\end{figure}
